Inference methods comparison for the simplified Naomi model

### 2023-03-27 src/naomi-simple_compare/comparison.Rmd
ks_plot working for model outputs too #24

ks_lambda_t1_out <- to_ks_df(par = "lambda_t1_out", outputs = TRUE, id = mf_out_fine$id) %>%
  merge_to_mf_out_fine()
```

>>>>

ks_lambda_t1_out <- to_ks_df(par = "lambda_t1_out", outputs = TRUE, id = mf_out_fine$id) %>%
  merge_to_mf_out_fine()

ks_plot(ks_df = ks_rho_t1_out, par = "rho_t1_out")
ks_plot(ks_df = ks_alpha_t1_out, par = "alpha_t1_out")
ks_plot(ks_df = ks_lambda_t1_out, par = "lambda_t1_out")
```
